Blame and Coercion: Together Again for the Second Time

### 2019-10-17 paper.tex
minor fix
starting para of sec 4

This section presents our first contribution, hypercoercion (HC). 
\figref{fig:hypercoercion} defines the syntax of HC.
Types, pre-types, and blame labels are as before.

@@

This section presents our second contribution, a space-efficient CEK abstract 
machine. This machine is parameterized over \emph{cast representation}.

@@

@@

		\item $ applyCast(cast(\POOprod{T_1}{T_2},l,T_3 \times 
		T_4),\hcvOOcons{v_1}{c_1}{v_2}{c_2}) $ \\
		$ = 
		\rOOsucc{(\hcvOOcons{v_1}{seq(c_1,cast(T_1,l,T_3))}{v_2}{seq(c_2,cast(T_2,l,T_4))})}
		$ 
		\item $ 
		applyCast(cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}),\hcvOOinl{v}{c})
		= \rOOsucc{(\hcvOOinl{v}{seq(c,cast(T_1,l,T_2))})} $
		\item $ 
		applyCast(cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}),\hcvOOinr{v}{c})
		= \rOOsucc{(\hcvOOinr{v}{seq(c,cast(T_3,l,T_4))})} $
	\end{enumerate}
\end{definition}

>>>>

This section presents our first contribution, the definition of hypercoercion. 
The functions that construct hypercoercions are deferred to subsections because 
they depend on blame strategies.
And the functions that apply hypercoercions to values are deferred to 
Section~\ref{sec:hypercoercion-correctness} because 
they depends on a new definition of values, which is part of the framework in
Section~\ref{sec:framework}.

\figref{fig:hypercoercion} defines the syntax of hypercoercion. Types, 
pre-types, and blame labels are as before.

@@

This section presents our second contribution, a framework for proving 
correctness of cast representations.
In subsection~\ref{ssec:framework:cek}, we introduce \effCEK{C}, a family 
of semantics (in the style of CEK machines) indexed by cast representations ($ 
C $). 
In subsection~\ref{secc:framework:bisim}, we prove when $ C $ is 
$ surely \; \text{\lazyD} $, $ \judgeDeval{e}{o} $ if and only $ 
\judgeSeval{C}{e}{o} $, that is, every $ surely \text{\lazyD} $ cast 
representation respects the \lazyD\ cast calculus. 
Proving a similar theorem for \lazyUD\ is in progress.

\subsection{A Space-efficient CEK machine}
\label{ssec:framework:cek}

We define cast representations and \effCEK{C}

space-efficient CEK abstract 
machine. This machine is parameterized over \emph{cast representation}.

@@

\subsection{Correctness Proof of Surely \lazyD\ Cast Representations}
\label{ssec:framework:correctness}

\todo[inline]{KC needs to move some content in the next section to here. -KC}

@@

		\item $ applyCast(cast(\POOprod{T_1}{T_2},l,T_3 \times 
		T_4),\hcvOOcons{v_1}{c_1}{v_2}{c_2}) $ \\
		$ = 
		\rOOsucc{(\hcvOOcons{v_1}{seq(c_1,cast(T_1,l,T_3))}{v_2}{seq(c_2,cast(T_2,l,T_4))})}
		$ 
		\item $ 
		applyCast(cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}),\hcvOOinl{v}{c})
		= \rOOsucc{(\hcvOOinl{v}{seq(c,cast(T_1,l,T_3))})} $
		\item $ 
		applyCast(cast(\POOsum{T_1}{T_2},l,\POOsum{T_3}{T_4}),\hcvOOinr{v}{c})
		= \rOOsucc{(\hcvOOinr{v}{seq(c,cast(T_2,l,T_4))})} $
	\end{enumerate}
\end{definition}
